### 2021-02-17 input/proposal.tex
algos mostly
slight changes, not much

\TODO{Remember to say stateless, asynchronous system.}

@@

Each process works autonomously and each change is broadcast to its
neighborhood, for neighbors may depend on this change as well.

% The main idea is maintaining graphs of partitions using local
% knowledge only and use graphs as often as possible: it improves
% resilience to crashes, convergence speed etc. Unfortunately,
% maintaining graphs of partitions in dynamic networks may require the
% use of broadcast tree. The removal of a communication channel between
% 2 processes may remove an advantageous path from processes downstream
% to the source of the partition they belong to.

This section describes \NAME's components by starting from the
simplest case of add-only partition, to the most complex case of
dynamic partitions in dynamic networks.

\TODO{Probably better to pair operation as ``ins, del'' and ``add, rem''?}

@@

\paragraph{Static network with add-only.}
At any time, a process can become a source, hence \TODO{creating} a
new partition in the system. This partition eventually includes all
processes that are closer from this new source than any other else. We
described such protocol in Section~\ref{sec:background}. Processes
naturally converge towards their respective best partition by only
piggybacking a monotonically increasing distance in forwarded
messages.  \TODO{Traffic of each partition is contained to the
  partition.}

\paragraph{Static network with dynamic partitions.}
At any time, a source can revoke its self-appointed status of source,
hence \TODO{removing} its partition of the system. All processes that
belong to this partition must choose another partition to belong to.

\noindent Since the number of partitions does not monotonically
increase in the system any longer, they require a vector of versions
that monotonically increases over \TODO{add and del} operations. This
allows processes to quickly discard stale messages saving
bandwidth. For instance, a process that received a message originated
at Process $a$ with a version $2$ knows that any message originated at
Process $a$ with a version $1$ are stale system-wide; it must not
forward it. As consequence, vectors of versions also ensure
termination, for messages \TODO{add and del} cannot follow each other
in an infinite loop. In terms of traffic, this only requires each
\TODO{delete} message to piggyback a source identifier and version
number.

@@

\paragraph{Networks with new communication links.}
Adding new communication links to the network may create shortcuts
between processes. Both processes must send their current best
partition to each other. Upon receipt, they act normally: if a process
finds out that the received partition is closer than its current one,
it delivers it which in turns also triggers another competition
amongst neighbors due to forwarding.

@@

\paragraph{Dynamic networks with dynamic partitions.}
When removing a communication link between two processes does not
break any active path, because neither distances of processes depend
on the other, then nothing needs to be done. \NAME has no overhead.
Unfortunately, when a process' distance depends on the other process,
the protocol becomes much more complex. Indeed, this requires to
\TODO{undo} all add messages originated from this process. A message
must convey the fact that
\begin{inparaenum}[(i)]
\item an edge at a particular process has been removed, and
\item the distance that has been delivered by a process comes from
  this particular process.
\end{inparaenum}

@@

\paragraph{A last optimisation}
\TODO{Carry information that is useless. such as order of processes in
  paths, and identities of processes themselves.} \TODO{Icarus for
  dissemination trees~\cite{whitaker2002forwarding}}. \TODO{No need to
  know the dimension of networks and
  partitions~\cite{almeida2007scalable}}.

>>>>

@@

Each process is stateless, works autonomously and asynchronously, in a
peer-to-peer fashion. Each process broadcasts each change to its
neighborhood, for the state of its neighbors may depend on this change
as well. Yet, generated traffic remains \TODO{low} using scoped
flooding. Messages that carry changes travel through the network
depending on partition of processes, stopping as soon as they
encounter uninterested processes. We demonstrate that \NAME guarantees
consistent partitioning despite different order in message deliveries
from one process to another.

This section describes \NAME's components and algorithms. First, it
starts by detailing a logical partitioning protocol in static
network. Second, it extends such protocol to dynamic systems. Last, it
describes an optimization based on Bloom filter.

@@

\subsection{Dynamic partitions}

At any time, a process can become a source, hence adding a new
partition to the system. This partition eventually includes all
processes that are closer from this new source than any other else. We
described such protocol in Section~\ref{sec:background}. Processes
naturally converge towards their respective best partition by only
piggybacking a monotonically increasing distance in forwarded
messages. % \TODO{Traffic of each partition is contained to the
%  partition.}

Then, at any time, a source can revoke its self-appointed status of
source, hence deleting its partition from the system. All processes
that belong to this partition must eventually choose another partition
to belong to. Since the number of partitions does not monotonically
increase in the system any longer, each process requires a vector of
versions that monotonically increases over delivered operations.

This allows processes to quickly discard stale messages saving
bandwidth. For instance, a process that received a message originated
at Process $a$ with a version $2$ knows that any message originated at
Process $a$ with a version $1$ are stale system-wide; it must not
forward it. As consequence, vectors of versions also ensure
termination, for messages \TODO{add and del} cannot follow each other
in an infinite loop. In terms of traffic, this only requires each
\TODO{delete} message to piggyback a source identifier and version
number.

@@

\subsection{Dynamic networks}
Adding new communication links to the network may create shortcuts
between processes. Both processes must send their current best
partition to each other. Upon receipt, they act normally: if a process
finds out that the received partition is closer than its current one,
it delivers it which in turns also triggers another competition
amongst neighbors due to forwarding.

@@

\begin{algorithm}
  \input{input/algoedges.tex}
  \caption{\label{algo:edges}Dynamic partitioning by Process $p$ in dynamic networks.}
\end{algorithm}

When removing a communication link between two processes does not
break any active path, because neither distances of processes depend
on the other, then nothing needs to be done. \NAME has no overhead.
Unfortunately, when a process' distance depends on the other process,
the protocol becomes much more complex. Indeed, this requires to
\TODO{undo} all add messages originated from this process. A message
must convey the fact that
\begin{inparaenum}[(i)]
\item an edge at a particular process has been removed, and
\item the distance that has been delivered by a process comes from
  this particular process.
\end{inparaenum}

@@

\subsection{A last optimization}
\TODO{Carry information that is useless. such as order of processes in
  paths, and identities of processes themselves.} \TODO{Icarus for
  dissemination trees~\cite{whitaker2002forwarding}}. \TODO{No need to
  know the dimension of networks and
  partitions~\cite{almeida2007scalable}}.
